Local Search Approximation Algorithms for Partitional and Hierarchical Clustering

### 2015-04-30 tex/project.tex
Paper Error
Fixed typo in paper
added writeup on datasets.  Still needs more after I talk to alice

Suppose we have a set of data $X$ of which we want to choose a subset $S$ such that $|S| \leq k$ so as to minimize 
\[ f(S) = \sum_{i \in X} \min_{j \in S} d(i,j) ,\]
where we can think of $d$ as some measure of dissimilarity (for example squared distance or absolute distance). For completeness, we define $f(\emptyset) = \min_{j \in S} f(\{j\})$. 
Note that this generalizes the $k$-median problem and can capture a variant of $k$-means in which we are restricted to choosing data points as centers.

@@

This algorithm first defines linear and submodular functions on $X$:
\begin{align*}
l(A) &= \sum_{j \in A} f(\{j\}) - f(\emptyset), \\
g(A) & = - l(A) - f(X \setminus A).
\end{align*}
Furthermore, we let $\hat{v}_g = \max_{j \in X} g(\{j\})$, $\hat{v}_l = \max_{j \in X} |l(\{j\})|$, and $\hat{v} = \max(\hat{v}_g , \hat{v}_l)$.

@@

>>>>

Suppose we have a set of data $X$ of which we want to choose a subset $S$ such that $|S| \leq k$ so as to minimize 
\[ f(S) = \sum_{i \in X} \min_{j \in S} d(i,j) ,\]
where we can think of $d$ as some measure of dissimilarity (for example squared distance or absolute distance). For completeness, we define $f(\emptyset) = \max_{j \in S} f(\{j\})$. 
Note that this generalizes the $k$-median problem and can capture a variant of $k$-means in which we are restricted to choosing data points as centers.

@@

This algorithm first defines linear and submodular functions on $X$:
\begin{align*}
l(A) &= \sum_{j \in A} \left [ f(\{j\}) - f(\emptyset) \right], \\
g(A) & = - l(A) - f(X \setminus A).
\end{align*}
Furthermore, we let $\hat{v}_g = \max_{j \in X} g(\{j\})$, $\hat{v}_l = \max_{j \in X} |l(\{j\})|$, and $\hat{v} = \max(\hat{v}_g , \hat{v}_l)$.

@@

\section{Data Sets}
In order to empirically test these clustering methods, we used four different data sets.  
\begin{description}
\item[Generated Gaussian Data] We wanted to test our clustering algorithms on data that had data nicely clustered around $k$ centers. So, we generated synthetic $k$-center Gaussian data algorithmically and used this for testing.
\item[$P$-median]
\item[UCI Iris Dataset] This is one of the most used data sets in pattern recognition (\cite{Iris}).  It contains data on 150 instances of flowers, each of with belongs to one of three species of iris.  One of the species is linearly seperable from the others, but the other two are not.  In total, there are 150 instances and 4 attributes.
\item[UCI Soybean Dataset] This is another small, real data set from UCI.  This, too, is widely used in machine learning.  It has 47 instances, with 35 attributes.
\end{description}
